Bullet Groups as a test of $\Lambda$CDM

### 2014-03-04 paper/ms.tex
first subsection

\newcommand{\avg}[1]{\langle{#1}\rangle}  
\newcommand{\hMpc}{{\ifmmode{h^{-1}{\rm Mpc}}\else{$h^{-1}$Mpc }\fi}}  
\newcommand{\hGpc}{{\ifmmode{h^{-1}{\rm Gpc}}\else{$h^{-1}$Gpc }\fi}}  
\newcommand{\hmpc}{{\ifmmode{h^{-1}{\rm Mpc}}\else{$h^{-1}$Mpc }\fi}}  
\newcommand{\hkpc}{{\ifmmode{h^{-1}{\rm kpc}}\else{$h^{-1}$kpc }\fi}}  
\newcommand{\hMsun}{{\ifmmode{h^{-1}{\rm {M_{\odot}}}}\else{$h^{-1}{\rm{M_{\odot}}}$}\fi}}  
\newcommand{\hmsun}{{\ifmmode{h^{-1}{\rm {M_{\odot}}}}\else{$h^{-1}{\rm{M_{\odot}}}$}\fi}}  
\newcommand{\Msun}{{\ifmmode{{\rm {M_{\odot}}}}\else{${\rm{M_{\odot}}}$}\fi}}  
\newcommand{\msun}{{\ifmmode{{\rm {M_{\odot}}}}\else{${\rm{M_{\odot}}}$}\fi}}  
\newcommand{\kms}{{\ifmmode{{\mathrm{\,km\ s}^{-1}}}\else{\,km~s$^{-1}$}\fi}}
\newcommand{\bullb}{MACS J0025.4-1222}
\newcommand{\bulla}{1E0657---56} 
\shorttitle{Bullet Groups}
\shortauthors{Fern\'andez-Trincado et al.}

@@

\subsection{Separations and Relative Circular Velocities}
\label{fig:separations}

@@

\begin{figure*}
\begin{center}
\includegraphics[width=1.0\textwidth]{Figures_eps/figure_7_2.eps}
\includegraphics[width=1.0\textwidth]{Figures_eps/figure_7_3.eps}
\end{center}
\caption{Scatter $\left(\frac{v_{circ,sub}}{v_{circ,halo}}\right)$
  vs $d_{2d,(X,Y)}$ for different redshifts. The  horizontal dashed
  line correpond to
  $\left(\frac{v_{circ,sub}}{v_{circ,halo}}\right)=0.5$ and the
  red star simbol correspond to
  $\left(\frac{v_{circ,sub}}{v_{circ,halo}}\right)=0.54$ for SL2S
  SJ08544-0121 in \citet{2013A&A...552A..80M}. The  four top panels
  are the sample with circular velocities $>700$ kms$^{-1}$ and the
  four down panels are the sample with  circular velocities between
  300 km s$^{-1}$ to 700 kms$^{-1}$.} 
\label{newparameter}
\end{figure*}

\begin{figure*}
\begin{center}
\includegraphics[width=1.1\textwidth]{Figures_eps/figure_7_1.eps}
\end{center}
\caption{Cumulative distribution (P$>d_{2d,(X,Y)}$) of displacements
  for the projection (X,Y). {\bf Left panel:} Sample with
  $v_{max}>700$ kms$^{-1}$  for different redshifts. The vertical
  dashed line, correspond to the separation between dark matter to
  dark matter estimate in this work as the double of separation
  between the collisional gas and dark matter of 124$\pm$20 kpc
  reported by \citet{Gastaldello} for the group SL2S J08544-0121.
  {\bf Right panel:} Sample with $300 $ kms$^{-1} <v_{max}<700 $
  kms$^{-1}$ for different redshifts.}  
\label{displacements}
\end{figure*}

>>>>

\newcommand{\avg}[1]{\langle{#1}\rangle}  
\newcommand{\hMpc}{{\ifmmode{h^{-1}{\rm Mpc}}\else{$h^{-1}$Mpc }\fi}}  
\newcommand{\hGpc}{{\ifmmode{h^{-1}{\rm Gpc}}\else{$h^{-1}$Gpc }\fi}}  
\newcommand{\hmpc}{{\ifmmode{h^{-1}{\rm Mpc}}\else{$h^{-1}$Mpc }\fi}}  
\newcommand{\hkpc}{{\ifmmode{h^{-1}{\rm kpc}}\else{$h^{-1}$kpc }\fi}}  
\newcommand{\hMsun}{{\ifmmode{h^{-1}{\rm {M_{\odot}}}}\else{$h^{-1}{\rm{M_{\odot}}}$}\fi}}  
\newcommand{\hmsun}{{\ifmmode{h^{-1}{\rm {M_{\odot}}}}\else{$h^{-1}{\rm{M_{\odot}}}$}\fi}}  
\newcommand{\Msun}{{\ifmmode{{\rm {M_{\odot}}}}\else{${\rm{M_{\odot}}}$}\fi}}  
\newcommand{\msun}{{\ifmmode{{\rm {M_{\odot}}}}\else{${\rm{M_{\odot}}}$}\fi}}  
\newcommand{\kms}{{\ifmmode{{\mathrm{\,km\ s}^{-1}}}\else{\,km~s$^{-1}$}\fi}}
\newcommand{\bullb}{MACS J0025.4-1222}
\newcommand{\bulla}{1E0657---56} 
\newcommand{\bullg}{SL2S J08544-0121}
\shorttitle{Bullet Groups}
\shortauthors{Fern\'andez-Trincado et al.}

@@

\subsection{Displacements and Relative Circular Velocities}
\label{fig:displacement}

\begin{figure*}
\begin{center}
\includegraphics[width=0.8\textwidth]{Figures_eps/figure_7_1.eps}
\end{center}
\caption{Integrated probability distribution for the displacement
  between the host halo and its dominand sub-halo. The left panel
  shows the results in terms of the physical displacements and the
  right panel the same displacement normalized by the virial radius of
  the host halo. The continous line corrresponds to the halos in the
  group sample $V_{\rm c,host}>700\kms$ and the dashed lines to the 
  The vertical stripe corresponds to the estimate of the separation
  between the two dark matter clumps in the results reported by
  \citet{Gastaldello} for the group SL2S J08544-0121. The right panel
  shows the same results normalized by the virial radius of the host
  halo.} 
\label{fig:displacement}
\end{figure*}

\begin{figure*}
\begin{center}
\includegraphics[width=1.0\textwidth]{Figures_eps/figure_7_2.eps}
\end{center}
\caption{2D histogram in the plane $V_{\rm c,sub}/V_{\rm
    c,host}$-$d_{2D}$. The left panel corresponds to groups and the
  right panel to clusters. The circle with error bars corresponds to
  \bullg data reported from \citet{2013A&A...552A..80M} and
  \citet{Gastaldello}. The data used to construct the histograms
  integrates the objects at all redshifts. }
\label{fig:mass_displacement}
\end{figure*}

The main result of this paper is summarized in Figure
\ref{fig:displacement}, it presents the integrated
probability distribution for the displacement between the center of
the host halo and its dominant sub-halo. The left pannel shows
the displacement in physical units and the right pannel as a fraction
of the virial radius of the host halo.

Figure \ref{fig:displacement} shows the results for two different
populations; groups with $300\kms < V_{\rm c, host}<700\kms$ and
clusters with $V_{\rm c,host}>700\kms$. Additionally, this is
presented for all redshifts $z=0.0, 0.25, 0.5$ and $1.0$.

The panel with the physical displacements also shows a vertical stripe
with the estimated displacement for the Bullet-group reported by
\cite{Gastaldello}. Considering this system as consistent withe the
groups sample we see that a fraction of $\sim XX\pm XX\%$ of the groups
should present a displacement equal or larger than the one estimated
for \bullg. The panel with the normalized displacements shows a
distribution that can be considered close to universal in the sense
that the two samples (groups and clusters) at all redshifts present a
similar trend.[...]

Figure \ref{fig:mass_displacement} shows 2D histograms in a plane
composed by the ratio of the two circular velocities $V_{\rm c,
  sub}/V_{\rm c, host}$ and the physical displacements. In each of the
halo samples (left, groups; right, clusters) the two-dimensional
distributions are similar and have been therefore integrated to build
the 2D histogram.

On top of these 2D histograms there is an circle with error bars that
represents the observational estimates for the system \bullg. [...]

@@
